Token-level author diarization using clustering of stylistic contexts

### 2017-05-31 paper/paper.tex
Some small modifications

Equivalently, the codomain of the mapping can also be defined as a set of segmentations $\Sigma$. A segmentation $S\in \Sigma$ is a minimal set of segments, where each segment $s$ represents a set of consecutive tokens $\{t_i\}_{i=i_1}^{i_2}$ where each is assigned the same label. For a segmentation to be valid, the segments must cover all terms in the document and not overlap:
\begin{equation}
	\bigcup_{s\in S}s = T_D  \wedge \bigcap_{s\in S}s = \{\}.
\end{equation}
The correct mapping of a documents to the corresponding segmentations will be denoted with $\sigma: \Delta\rightarrow\Sigma$.

@@

% details for each component
\paragraph{Tokenization.} As a preprocessing step, we tokenized each document $D$ with \texttt{nltk}\footnote{\texttt{http://www.nltk.org}} toolkit, to obtain a set of tokens $T_D$. We also performed Part of Speech tagging with the same tool, to speed up a basic feature extraction which we describe below. We didn't use other preprocessing techniques such as lemmatization, stemming and stop word removal because they would take away a lot of stylometric data from text \cite{stamatatos-2009a}. The final output from tokenization step was a finite sequence $\{(t_i, o_i, l(t_i), POS_i)\}_{i=1}^n$ where $o_i$ is the offset of token $t_i$, $l(t_i)$ its length in characters and $POS_i$ its POS tag.

>>>>

Equivalently, the codomain of the mapping can also be defined as a set of segmentations $\Sigma$. A segmentation $S\in \Sigma$ is a minimal set of segments, where each segment $s$ represents a set of consecutive tokens $\{t_i\}_{i=i_1}^{i_2}$ where each token is assigned the same label. For a segmentation to be valid, the segments must cover all terms in the document and not overlap:
\begin{equation}
	\bigcup_{s\in S}s = T_D  \wedge \bigcap_{s\in S}s = \{\}.
\end{equation}
The correct mapping of a documents to the corresponding segmentations will be denoted with $\sigma: \Delta\rightarrow\Sigma$.

@@

% details for each component
\paragraph{Tokenization.} As a preprocessing step, we tokenized each document $D$ using NLTK\footnote{\url{http://www.nltk.org}} to obtain a set of tokens $T_D$. We also performed part-of-speech tagging with the same tool, to speed up basic feature extraction which we describe below. We didn't use other preprocessing techniques such as lemmatization, stemming and stop word removal because they would take away a lot of stylometric data from text \cite{stamatatos-2009a}. The final output from the tokenization step was a finite sequence $\{(t_i, o_i, l(t_i), \mathit{POS}_i)\}_{i=1}^n$ where $o_i$ is the offset of token $t_i$, $l(t_i)$ its length in characters and $\mathit{POS}_i$ its POS tag.
